### 2019-07-05 report/MSc_Report.tex
adjustments after correction

\section{Small Study Effect and Excess of Significance Tests} \label{sec:publication.bias.tests}

The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small study effects tests and excess significance tests. The direction in which bias is expected is the one on which more significant results are ($p$-value < 0.05, two-sided). The tests are applied on the original effect size measures, i.e. risk ratios, Hedges $g$ or log hazard ratios. Different tests are applied depending on the outcome type being binary or continuous and survival.\\
Thus, multiple tests are applied on the same data. The results can then be displayed separately to compare the results from the different tests. A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}. \\
``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}. For continuous and survival outcomes, the names refer to:

\end{knitrout}
\caption{Histogram of one-sided $p$-values for small study effect in direction of larger effect sizes. The testing method is indicated in the header, bin width is equal to 0.1. The significant proportion based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test}
\end{figure}

%Agreement table -> Chunck 1
The histograms in Figure \ref{fig:test} show that most distributions are clearly skewed to the right, indicating evidence for small study effects. Exceptions from this are the excess significance and Schwarzer's test, and the tests for survival outcomes. There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer). But note that the sample size of survival outcomes is small ($n$ = 39). \\
There is discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger. Also, we see that the $I^2$ statistic of the proportion of overall between-study heterogeneity is distributed differently for the tests, with results with $I^2 = 0$ being evenly distributed in binary outcomes along the range of $p$-values, while they are more similar to the meta-analyses with larger heterogeneity for continuous outcome.\\
In the literature, the excess significance test is advised to be used in the case of no between study heterogeneity. Since there are no small $p$-values for such meta-analyses, one must conclude that there is no excess significance in the dataset. The obvious correspondence with the heterogeneity statistic however rather suggests that the test itself is just another was to assess between study heterogeneity. Thompson test and R\"ucker's test are designed such that they take into account the between study heterogeneity when assessing small study effects. When no heterogeneity is given, Thompsons test results and Eggers test result should be equal, however, the $I^2$ statistic is computed by a more suitable estimator \citep{paulemandel} of $\tau^2$ as the estimator that Thompson and Sharp's test uses (method of moment estimator of \citet{tau.estimator}, which is more conservative by usually finding larger $\tau^2$). In the part of the histogram with $I^2 > 0$, the two tests are more reliable than the remaining tests, while the opposite is expected from simulations \citep{limitmeta} when $I^2 = 0$.\\

It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects for the same meta-analyses. A simple method to check the coincidence of test results is to compare scatterplots and empirical Spearman correlations between the test statistics. This is done in Figure \ref{fig:test.agreement}. Here, there is no separation between survival and continuous outcomes. The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results. Also, the $I^2$ statistic is included. Since no test statistic is used for excess significance tests, it is not shown here

The observed patterns on the scatterplots differ, and some small study effect test statistics do align better than others. Regression based tests as Egger and Thompsons test which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients. Continuous and survival outcome type tests align more closely than binary outcome tests. While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics .\\
Because scatterplots and correlation coefficients can be misleading, also a Tukey mean-difference or Bland-Altman of transformed $p$-values plot is shown for four scenarios in Figure \ref{fig:mean.diff.test}:
\begin{itemize}
\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
\item For Egger's and excess significance tests
\item For Harbord's and R\"ucker's tests
\item For Harbord's and excess significance tests
\end{itemize}

\begin{itemize}
\item the mean of the differences should be around zero (systematic error) 
\item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible
\end{itemize}

Although this is not formally tested, there are likely systematic errors and bias between excess significance tests, although more so for continuous tests. -- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- \\
The confidence intervals can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests. This suggests that correspondence between the tests is not very good in general.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Jul  2 18:53:37 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{ccc}
  \hline
Count & Binary Outcomes & Continuous and Survival \\ 
  \hline
0 & 68 \% & 64.3 \% \\ 
  1 & 13.5 \% & 10 \% \\ 
  2 & 7.5 \% & 6.9 \% \\ 
  3 & 5.2 \% & 16.5 \% \\ 
  4 & 4.9 \% & 2.3 \% \\ 
  5 & 0.8 \% & - \\ 
   \hline
\end{tabular}
\endgroup
\caption{Counts Number of significant test results per meta-analysis, separated
       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
       applied} 
\label{number.sig.tests}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Jul  2 18:53:53 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lcccccccccr}
  \hline
 & 5\% & 25\% & 50\% & 75\% & 95\% & mean & = 0 (\%) & $>$= 0 (\%) & $>$ 0 (\%) & No adj. est. (\%) \\ 
  \hline
z: Fixed - Copas & -0.05 & -0.01 & -0.00 & 0.01 & 0.05 & -271.73 & 4.76 & 48.67 & 43.91 & 71.54 \\ 
  z: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.04 & -263.62 & 71.65 & 89.42 & 17.77 & 71.54 \\ 
  z: Fixed - Regression & -0.13 & -0.03 & 0.01 & 0.05 & 0.14 & 0.01 & 0.00 & 52.44 & 52.44 & 0.17 \\ 
  z: Random - Regression & -0.15 & -0.03 & 0.02 & 0.07 & 0.18 & 0.02 & 0.00 & 57.64 & 57.64 & 0.17 \\ 
  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.09 & 0.02 & 22.76 & 59.14 & 36.38 & 60.96 \\ 
  g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.14 & 0.03 & 63.29 & 87.49 & 24.20 & 60.96 \\ 
  g: Fixed - Regression & -0.23 & -0.04 & 0.03 & 0.13 & 0.38 & 0.05 & 0.00 & 61.96 & 61.96 & 0.00 \\ 
  g: Random - Regression & -0.24 & -0.03 & 0.05 & 0.16 & 0.42 & 0.06 & 0.00 & 64.06 & 64.06 & 0.00 \\ 
  Log h.r.: Fixed - Copas & -0.02 & 0.00 & 0.00 & 0.00 & 0.02 & -0.00 & 46.15 & 35.90 & 82.05 & 56.41 \\ 
  Log h.r.: Random - Copas & -0.02 & 0.00 & 0.00 & 0.00 & 0.00 & -0.01 & 61.54 & 17.95 & 79.49 & 56.41 \\ 
  Log h.r.: Fixed - Regression & -0.20 & -0.13 & -0.06 & 0.02 & 0.14 & -0.05 & 0.00 & 33.33 & 33.33 & 0.00 \\ 
  Log h.r.: Random - Regression & -0.22 & -0.14 & -0.07 & 0.03 & 0.14 & -0.06 & 0.00 & 33.33 & 33.33 & 0.00 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects. The column with the names ``> 0'' give the percentages of estimates larger than zero or larger or equal zero. The column ``No adj. est.'' gives the percentage of missing estimates due to non-significant publication bias test (for Copas) and computational errors. The row names indicate which outcome measure, meta-analysis method and adjustment method is used. Abbreviations are used for z-score (= z) and Hedges g (= g).} 
\label{adjustment.difference}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Jul  2 18:53:54 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lrrrrrrr}
  \hline
 & = 0 & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
  \hline
Missing fraction & 323 & 0 & 0 & 0.1 & 0.3 & 1.0 & 0.2 \\ 
  Missing study number & 323 & 0 & 0 & 1.4 & 5.2 & 17.9 & 4.2 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.} 
\label{copas.missing}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Tue Jul  2 18:53:54 2019
\begin{table}[ht]
\centering
\begingroup\tiny
\begin{tabular}{lcccrrrrrrrr}
  \hline
meta.id & file.nr & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
  \hline
2009 & 2009 & 1 & 1 & 0.31 & 0.36 & 0.31 & 0.43 & 0.70 & 0.70 & 0.70 & 2.48 \\ 
  2068 & 2068 & 2 & 0 & 0.29 & 0.35 & 0.29 & 0.42 & 0.68 & 0.68 & 0.68 & 2.57 \\ 
  52528 & 52528 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
  60546 & 60546 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
  70389 & 70389 & 1 & 1 & -0.08 & -0.07 & 15.62 & -0.04 & -0.13 & -0.13 & -0.13 & -0.05 \\ 
  73769 & 73769 & 3 & 1 & -0.09 & 0.00 & 7148.96 & 0.02 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
  79113 & 79113 & 2 & 0 & -0.38 & -0.38 & -0.38 & -0.48 & -0.93 & -0.93 & -2.00 & -3.47 \\ 
  90138 & 90138 & 3 & 0 & 0.30 & 0.80 & 0.30 & 0.53 & 0.72 & 0.71 & 0.71 & 2.16 \\ 
  97356 & 97356 & 2 & 0 & -0.06 & -0.33 & -0.06 & -0.11 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
  98030 & 98030 & 1 & 0 & -0.09 & -0.07 & -0.09 & -0.04 & -0.41 & -0.41 & -1.50 & -2.79 \\ 
  101436 & 101436 & 1 & 5 & 0.54 & 0.62 & 0.80 & 0.90 & 1.21 & 1.21 & 1.21 & 2.74 \\ 
  118121 & 118121 & 4 & 1 & 0.25 & 0.23 & 47.73 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
  119537 & 119537 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
  119818 & 119818 & 3 & 3 & -0.25 & -0.25 & -0.20 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
  146301 & 146301 & 1 & 0 & 0.14 & 0.26 & 472149.03 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects. Abbreviations are used for z-score (= z) and Hedges g (= g).} 
\label{missing.differences}
\end{table}

No formal tests are provided, but the at least there seems to be no clear bias or systematic error. The limits of agreement in Figure \ref{fig:adjustment.mean.diff} are large. We conclude thus that the impact of regression adjustment on the effect sizes is in general not substantially larger than the impact of Copas selection model in the subset of data where the estimate of the Copas selection model is not equal to a random effects estimate.  \\

% LaTeX file for Chapter 04

\chapter{Methods} 
\section{Introduction and Notation}
The analysis has already been said to be restricted on clinical or health care interventions. The interventions are restricted to comparisons of two treatment arms by some measure of sanity or worsening of health. The difference in this measure between the groups is referred to as the treatment effect. Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or Hedges $g$, Fisher's z score or Pearsons correlation coefficient. \\
Let us consider a meta-analysis with $n$ study treatment effects ($n > 1$, but typically small). A study is indexed by $i$, and it's treatment effect by  $\theta_i$. The observed treatment effect is $\hat{\theta}_i$. The pooled treatment effect of a meta-analysis will be denoted as $\theta_M$, and consequently, the observed pooled treatment effect as $\hat{\theta}_M$. Furthermore, each treatment effect is typically measured with some standard error $\se_i$ and an estimate of $\se_i$ is denoted as $\hat{\se}_i$. The $\hat{}$ sign thus indicates if it is an estimate.\\
For continuous outcomes, let $m_t$ be the mean of the treatment group, $m_c$ the mean of the control group, and equivalently $\textrm{sd}_t$ and $\textrm{sd}_c$ the corresponding standard deviations. $n_t$ and $n_c$ are the total number of participants in the groups.
In the case of binary outcomes, let $e_t$ be the count of events in the treatment arm $e_c$ the count of events in the control group. The observed counts in a study $i$ are referred to as $e_{t,i}$ and analogously $e_{c,i}$.

@@

\begin{align}
I^2 &= \max\big(0, 1 - \frac{n-1}{Q}\big) \nonumber%\label{I2.proportion}
\end{align}

@@

>>>>

\chapter{Methods} \label{ch:methods}
\section{Introduction and Notation}
The analysis has already been said to be restricted on clinical or health care interventions. The interventions are restricted to comparisons of two treatment arms by some measure of sanity or worsening of health. The difference in this measure between the groups is referred to as the treatment effect. Where it is not particularly mentioned, the term treatment effect refers to any effect measure such as log risk ratio, log hazard ratio, Cohen's $d$ or Hedges $g$, Fisher's z score or Pearsons correlation coefficient. \\
Let us consider a meta-analysis with $n$ study treatment effects ($n > 1$, but typically small). A study is indexed by $i$, and it's treatment effect by  $\theta_i$. The observed treatment effect is $\hat{\theta}_i$. The pooled treatment effect of a meta-analysis will be denoted as $\theta_M$, and consequently, the observed pooled treatment effect as $\hat{\theta}_M$. Furthermore, each treatment effect is typically measured with some standard error $\se_i$ and an estimate of $\se_i$ is denoted as $\hat{\se}_i$. The $\hat{}$ sign thus indicates if it is an estimate.\\
For continuous outcomes, let $m_t$ be the mean of the treatment group, $m_c$ the mean of the control group, and equivalently $\textrm{sd}_t$ and $\textrm{sd}_c$ the corresponding standard deviations. $n_t$ and $n_c$ are the total number of participants in the groups.
In the case of binary outcomes, let $e_t$ be the count of events in the treatment arm $e_c$ the count of events in the control group. The observed counts in a study $i$ are referred to as $e_{t,i}$ and analogously $e_{c,i}$.

@@

\begin{align}
I^2 &= \max\Big(0, 1 - \frac{n-1}{Q}\Big) \nonumber%\label{I2.proportion}
\end{align}

@@

\section{Publication Bias Test Results} \label{sec:publication.bias.tests}

The meta-analyses fulfilling the criteria from chapter \ref{ch:dataset}, section \ref{sec:Processing}, are analysed with one-sided small study effects tests and excess significance tests. The direction in which bias is expected is the one on which more significant results are ($p$-value < 0.05, two-sided). The tests are applied on the original effect size measures, i.e. risk ratios, Hedges $g$ or log hazard ratios. Different tests are applied depending on the outcome type being binary, continuous or survival.\\
Thus, multiple tests are applied on the same data. The results can then be displayed separately to compare the results from the different tests. A histogram of $p$-values will summarize the overall evidence against the null-hypothesis of no publication bias, as displayed in Figure \ref{fig:test}. \\
``Excess significance'' denotes the excess of significant $p$-values testing method from \citet{excess.significance}, see \ref{sec:excess.significance}. For continuous and survival outcomes, the names refer to:

\end{knitrout}
\caption{Histogram of one-sided $p$-values for small study effect in direction of larger effect sizes. The testing method is indicated in the header, bin width is equal to 0.1. The proportion of meta-analyses with signifiant publication bias based on the threshold of 0.1 is displayed inside the figures.}
\label{fig:test}
\end{figure}

%Agreement table -> Chunck 1
The histograms in Figure \ref{fig:test} show that most distributions are clearly skewed to the right, indicating evidence for small study effects. Exceptions from this are the excess significance and Schwarzer's test, and the tests for survival outcomes. There, there is no evidence for publication bias, and the histograms are even skewed to the left (Schwarzer). But note that the sample size of survival outcomes is small ($n$ = 39). \\
There is discrepancy between continuous and binary data test results; the evidence for small study effects in continuous data is clearly larger. Also, we see that the $I^2$ statistic of the proportion of overall between-study heterogeneity is distributed differently for the tests, with results with $I^2 = 0$ being evenly distributed in binary outcomes along the range of $p$-values, while they are more similar to the meta-analyses with larger heterogeneity for continuous outcome.\\
In the literature, the excess significance test is advised to be used in the case of no between study heterogeneity. Since there are no small $p$-values for such meta-analyses, one must conclude that there is no excess significance in the dataset. The obvious correspondence with the heterogeneity statistic however rather suggests that the test is another way to assess between study heterogeneity. Thompson test and R\"ucker's test are designed such that they take into account the between study heterogeneity when assessing small study effects. When no heterogeneity is given, Thompson's test results and Egger's test result should be equal, however, the $I^2$ statistic is computed by a more suitable estimator \citep{paulemandel} of $\tau^2$ as the estimator that Thompson and Sharp's test uses (method of moment estimator of \citet{tau.estimator}, which is more conservative by usually finding larger $\tau^2$). In the part of the histogram with $I^2 > 0$, the two tests are more reliable than the remaining tests, while the opposite is expected from simulations \citep{limitmeta} when $I^2 = 0$.\\

It cannot be seen in Figure \ref{fig:test} if the tests used are finding small study effects for the same meta-analyses. A simple method to check the consistency of test results is to compare scatterplots and empirical Spearman correlations between the test statistics. This is done in Figure \ref{fig:test.agreement}. Here, there is no separation between survival and continuous outcomes. The upper left rectangle is displaying binary outcome results and the lower right continuous and survival outcomes results. Also, the $I^2$ statistic is included. Since no test statistic is used for excess significance tests, it is not shown here

The observed patterns on the scatterplots differ, and some small study effect test statistics do align better than others. Regression based tests as Egger and Thompsons test which are methodically almost identical are closely aligned, which is reflected in large correlation coefficients. Continuous and survival outcome type tests align more closely than binary outcome tests. While correlation coefficients between binary outcome tests vary between each other, Harbord's test statistic has similar correlation coefficients with the other small study effect test statistics.\\
Because scatterplots and correlation coefficients can be misleading, also a Tukey mean-difference or Bland-Altman of transformed $p$-values plot is shown for four scenarios in Figure \ref{fig:mean.diff.test}:
\begin{itemize}
\item For Egger's and Thompson's tests, which is supposedly the most similar test and should show the least deviations and systematic errors
\item For Egger's and excess significance tests
\item For Harbord's and R\"ucker's tests
\item For Harbord's and excess significance tests
\end{itemize}

\begin{itemize}
\item the mean of the differences should be around zero (no systematic error) 
\item the points should scatter independently on the $y$-axis and no general increase or decrease with the mean of the transformed $p$-values should be visible
\end{itemize}

Although this is not formally tested, there are likely systematic errors and bias between excess significance tests, although more so for continuous tests. -- In the appendix, it can be seen that this is reproducible with the remaining small study effect tests (not there yet) -- \\
The confidence intervals from Figure \ref{fig:mean.diff.test} can be used as limits of agreement, which gives, after back-transformation, around 0.9 for Egger's and Thompson's test, and around 0.99 for Harbord's and R\"ucker's tests. This suggests that correspondence between the tests is not very good in general.

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Jul  5 16:13:26 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{ccc}
  \hline
Count & Binary Outcomes & Continuous and Survival \\ 
  \hline
0 & 68 \% & 64.3 \% \\ 
  1 & 13.5 \% & 10 \% \\ 
  2 & 7.5 \% & 6.9 \% \\ 
  3 & 5.2 \% & 16.5 \% \\ 
  4 & 4.9 \% & 2.3 \% \\ 
  5 & 0.8 \% & - \\ 
   \hline
\end{tabular}
\endgroup
\caption{Counts Number of significant test results per meta-analysis, separated
       for outcome types. Last entry for continuous and survival outcomes is empty since one test less was 
       applied} 
\label{number.sig.tests}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Jul  5 16:13:41 2019
\begin{table}[ht]
\centering
\begingroup\scriptsize
\begin{tabular}{lcccccccccr}
  \hline
 & 5\% & 25\% & 50\% & 75\% & 95\% & mean & = 0 (\%) & $>$= 0 (\%) & $>$ 0 (\%) & No adj. est. (\%) \\ 
  \hline
z: Fixed - Copas & -0.05 & -0.01 & -0.00 & 0.01 & 0.05 & -271.73 & 4.76 & 48.67 & 43.91 & 71.54 \\ 
  z: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.04 & -263.62 & 71.65 & 89.42 & 17.77 & 71.54 \\ 
  z: Fixed - Regression & -0.13 & -0.03 & 0.01 & 0.05 & 0.14 & 0.01 & 0.00 & 52.44 & 52.44 & 0.17 \\ 
  z: Random - Regression & -0.15 & -0.03 & 0.02 & 0.07 & 0.18 & 0.02 & 0.00 & 57.64 & 57.64 & 0.17 \\ 
  g: Fixed - Copas & -0.05 & -0.01 & 0.00 & 0.01 & 0.09 & 0.02 & 22.76 & 59.14 & 36.38 & 60.96 \\ 
  g: Random - Copas & -0.00 & 0.00 & 0.00 & 0.00 & 0.14 & 0.03 & 63.29 & 87.49 & 24.20 & 60.96 \\ 
  g: Fixed - Regression & -0.23 & -0.04 & 0.03 & 0.13 & 0.38 & 0.05 & 0.00 & 61.96 & 61.96 & 0.00 \\ 
  g: Random - Regression & -0.24 & -0.03 & 0.05 & 0.16 & 0.42 & 0.06 & 0.00 & 64.06 & 64.06 & 0.00 \\ 
  Log h.r.: Fixed - Copas & -0.02 & 0.00 & 0.00 & 0.00 & 0.02 & -0.00 & 46.15 & 35.90 & 82.05 & 56.41 \\ 
  Log h.r.: Random - Copas & -0.02 & 0.00 & 0.00 & 0.00 & 0.00 & -0.01 & 61.54 & 17.95 & 79.49 & 56.41 \\ 
  Log h.r.: Fixed - Regression & -0.20 & -0.13 & -0.06 & 0.02 & 0.14 & -0.05 & 0.00 & 33.33 & 33.33 & 0.00 \\ 
  Log h.r.: Random - Regression & -0.22 & -0.14 & -0.07 & 0.03 & 0.14 & -0.06 & 0.00 & 33.33 & 33.33 & 0.00 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Quantiles and Means of the differences between meta-analysis pooled treatment effects and small study adjusted treatment effects. The column with the names ``> 0'' give the percentages of estimates larger than zero or larger or equal zero. The column ``No adj. est.'' gives the percentage of missing estimates due to non-significant publication bias test (for Copas) and computational errors. The row names indicate which outcome measure, meta-analysis method and adjustment method is used. Abbreviations are used for z-score (= z) and Hedges g (= g).} 
\label{adjustment.difference}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Jul  5 16:13:42 2019
\begin{table}[ht]
\centering
\begingroup\footnotesize
\begin{tabular}{lrrrrrrr}
  \hline
 & = 0 & 5\% & 25\% & 50\% & 75\% & 95\% & mean \\ 
  \hline
Missing fraction & 323 & 0 & 0 & 0.1 & 0.3 & 1.0 & 0.2 \\ 
  Missing study number & 323 & 0 & 0 & 1.4 & 5.2 & 17.9 & 4.2 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Fraction of missing studies and estimates of missing studies with their zero counts (``= 0''), quantiles and means.} 
\label{copas.missing}
\end{table}

% latex table generated in R 3.5.1 by xtable 1.8-3 package
% Fri Jul  5 16:13:42 2019
\begin{table}[ht]
\centering
\begingroup\tiny
\begin{tabular}{lcccrrrrrrrr}
  \hline
meta.id & file.nr & comparison.nr & subgroup.nr & z fixed & z random & z Copas & z regression & g fixed & g random & g Copas & g regression \\ 
  \hline
2009 & 2009 & 1 & 1 & 0.31 & 0.36 & 0.31 & 0.43 & 0.70 & 0.70 & 0.70 & 2.48 \\ 
  2068 & 2068 & 2 & 0 & 0.29 & 0.35 & 0.29 & 0.42 & 0.68 & 0.68 & 0.68 & 2.57 \\ 
  52528 & 52528 & 1 & 0 & -0.75 & -0.69 & -0.50 & -0.26 & -1.19 & -1.53 & 0.18 & -0.52 \\ 
  60546 & 60546 & 1 & 1 & 0.17 & 0.24 & 0.17 & 0.34 & 0.53 & 0.53 & 0.53 & 1.65 \\ 
  70389 & 70389 & 1 & 1 & -0.08 & -0.07 & 15.62 & -0.04 & -0.13 & -0.13 & -0.13 & -0.05 \\ 
  73769 & 73769 & 3 & 1 & -0.09 & 0.00 & 7148.96 & 0.02 & -0.01 & -0.12 & 0.01 & 0.04 \\ 
  79113 & 79113 & 2 & 0 & -0.38 & -0.38 & -0.38 & -0.48 & -0.93 & -0.93 & -2.00 & -3.47 \\ 
  90138 & 90138 & 3 & 0 & 0.30 & 0.80 & 0.30 & 0.53 & 0.72 & 0.71 & 0.71 & 2.16 \\ 
  97356 & 97356 & 2 & 0 & -0.06 & -0.33 & -0.06 & -0.11 & -0.42 & -0.35 & -1.58 & -1.82 \\ 
  98030 & 98030 & 1 & 0 & -0.09 & -0.07 & -0.09 & -0.04 & -0.41 & -0.41 & -1.50 & -2.79 \\ 
  101436 & 101436 & 1 & 5 & 0.54 & 0.62 & 0.80 & 0.90 & 1.21 & 1.21 & 1.21 & 2.74 \\ 
  118121 & 118121 & 4 & 1 & 0.25 & 0.23 & 47.73 & -0.03 & 0.44 & 0.44 & 0.44 & 0.14 \\ 
  119537 & 119537 & 3 & 0 & 0.07 & 0.15 & 0.07 & 0.29 & 0.50 & 0.50 & 1.43 & 1.81 \\ 
  119818 & 119818 & 3 & 3 & -0.25 & -0.25 & -0.20 & -0.04 & -0.50 & -0.54 & 28.44 & -0.03 \\ 
  146301 & 146301 & 1 & 0 & 0.14 & 0.26 & 472149.03 & 0.28 & 0.56 & 0.37 & 0.60 & 0.52 \\ 
   \hline
\end{tabular}
\endgroup
\caption{Missing meta-analysis pooled treatment effect and adjusted treatment effects. Abbreviations are used for z-score (= z) and Hedges g (= g).} 
\label{missing.differences}
\end{table}

No formal tests are provided, but the at least there seems to be no clear bias or systematic error. The limits of agreement in Figure \ref{fig:adjustment.mean.diff} are large. We conclude thus that the impact of regression adjustment on the effect sizes is in general not substantially larger than the impact of Copas selection model in the subset of data where the estimate of the Copas selection model is not equal to a random effects estimate. There is however a small difference, with regression estimates to have a little bit a larger absolute value. There might be some bias between adjusted $z$-scores, where regression estimates seem to be somewhat smaller when the mean is a little above zero, and somewhat larger when the mean is a little below zero. \\
